---
title: "REDCap + R: How to Do All the Things!"
description: A gentle introduction to using R with REDCap databases using the REDCapR and REDCapTidieR packages.
author:
  - name: Stephan Kadauke
    url: https://www.linkedin.com/in/skadauke/
    affiliation: Children's Hospital of Philadelphia
  - name: Will Beasley
    url: https://ouhsc.edu/bbmc/team/#willbeasley
    affiliation: Oklahoma University
format: 
  html:
    theme: flatly
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Welcome!

This is the website for the REDCapCon Deep Dive *REDCap + R: How to Do All the Things!*

You'll learn about [Quarto](https://quarto.org/), a framework for reproducible data science, and how to use REDCap with R to download projects, perform data analysis and visualization, and how to write data back to REDCap.

For the best experience, we suggest the following (none of the below are absolutely necessary!):

-   If available to you, use two monitors (or another two-screen setup such as a laptop and a tablet or two laptops).
-   We suggest you use a recent version of macOS or Windows - we have had issues with Linux.
-   We highly recommend you use the Google Chrome browser to access the Posit Cloud training environment.

## Pre-work

### Essential

-   Install the latest version of [Google Chrome](https://www.google.com/chrome/).
-   We will use Posit Cloud as a backup training environment. Please sign up for a free account [here](https://rstudio.cloud).

### Optional

-   Install [R](https://cloud.r-project.org/) and [RStudio Desktop](https://rstudio.com/products/rstudio/download/) on your computer. We made video with step by step instructions for installing these on macOS ([here](https://www.youtube.com/watch?v=GM88tYlEy_g)) or Windows ([here](https://www.youtube.com/watch?v=JRKmZK5-6aE)).
-   Here are the PowerPoint slides for download:
    -   [00 - Welcome](https://github.com/skadauke/redcapcon_2023_redcap_r_workshop/raw/main/slides/00_welcome.pptx)
    -   [01 - Extract and Explore](https://github.com/skadauke/redcapcon_2023_redcap_r_workshop/raw/main/slides/01_extract_explore.pptx)
    -   [02 - Transform and Visualize](https://github.com/skadauke/redcapcon_2023_redcap_r_workshop/raw/main/slides/02_transform_visualize.pptx)
    -   [03 - Advanced REDCapR](https://github.com/skadauke/redcapcon_2023_redcap_r_workshop/raw/main/slides/03_advanced_redcapr.pptx)
    -   [04 - Recreate and Extend](https://github.com/skadauke/redcapcon_2023_redcap_r_workshop/raw/main/slides/04_recreate_extend.pptx)

## Going through the course

We have recorded the session and made it available on [YouTube](TODO).

We have created an online training environment with interactive exercises that are referenced in the YouTube recording. The training environment can be accessed [here](https://posit.cloud/content/6465016).

The entire course should take about 2 hours to complete.

## After the course

If you would like to practice with the materials from the course, go to the [GitHub repository](https://github.com/skadauke/intro-to-r-for-clinical-data-rmed2022), and click the green button labeled "Code" to download the repository as a .ZIP file.

To install all the packages we used in the training environment, open RStudio and run the following command in the Console:

```{r, eval = FALSE, echo = TRUE}
install.packages(c(
  "tidyverse",
  "REDCapR",
  "REDCapTidieR"
))
```

## Resources

-   [REDCapR Documentation](https://ouhscbbmc.github.io/REDCapR/)
-   [REDCapTidieR Documentation](https://chop-cgtinformatics.github.io/REDCapTidieR/)
-   [R for Data Science](https://r4ds.hadley.nz/) (by Hadley Wickham, Mine Çetinkya-Rundel, and Garrett Grolemund)
-   [Quarto](https://quarto.org/)
-   [RStudio/Posit Cheatsheets](https://rstudio.com/resources/cheatsheets/)

## License

All of the material in this GitHub repository is copyrighted under the [Creative Commons BY-SA 4.0](https://creativecommons.org/licenses/by-sa/4.0/) copyright to make the material easy to reuse. We encourage you to reuse it and adapt it for your own teaching as you like!

## Acknowledgments {.appendix}

This course draws from various sources, most notably Garrett Grolemund's [Welcome to the Tidyverse](https://github.com/rstudio-education/welcome-to-the-tidyverse) and Greg Wilson's [Teaching Tech Together](http://teachtogether.tech/en/). This site was built using [Quarto](https://quarto.org/).
